### 2019-02-12 pkg/Pmisc/inst/docs/document.Rmd
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1752 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
subfigures fixed
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@2046 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

if(any(commandArgs()=='mdToTex')) {
# if you'll be converting md to tex, can use the following
  knitr::knit_hooks$set(plot=knitr::hook_plot_tex)  
  knitr::opts_chunk$set(
    out.width='0.45\\textwidth', 
    dev='pdf', fig.align='center')
  mdToTex = TRUE
} else {
  knitr::knit_hooks$set(plot=Pmisc::hook_plot_mdsubfig)
  knitr::opts_chunk$set(dev='png', out.width='40%')
  mdToTex = FALSE
}

@@

knitr::opts_chunk$set(
  echo=FALSE, prompt=TRUE, comment=NA,
  margins=1, fig.cap=' ', fig.pos='ht',
  fig.width=2.75, fig.height=2,  dpi=250, 
  tidy=TRUE, tidy.opts=list(indent=2, width.cutoff=55)
)

@@

# consider adding
automatic-styles = '<style:style style:name="OLE" style:family="graphic"><style:graphic-properties text:anchor-type="paragraph" style:wrap="none"/></style:style>'
# to make equations better in odt document
```

@@

```{r anotherplot, fig.ncol=3, fig.cap='Other uninteresting plots', fig.subcap=month.name[1:6], out.width=c('30%', '0.3\\textwidth')[1+mdToTex]}

>>>>

if(any(commandArgs()=='mdToTex')) {
# if you'll be converting md to tex, can use the following
  knitr::knit_hooks$set(plot=knitr::hook_plot_tex)  
  knitr::opts_chunk$set(
    out.width='0.45\\textwidth', 
    dev='pdf', fig.align='center')
  mdToTex = TRUE
} else {
  knitr::knit_hooks$set(plot=Pmisc::hook_plot_mdsubfig)
  knitr::opts_chunk$set(dev='png')
  mdToTex = FALSE
}

@@

knitr::opts_chunk$set(
  echo=FALSE, prompt=TRUE, comment=NA,
  margins=1, fig.cap=' ', fig.pos='ht',
  fig.width=5.5, fig.height=4, 
  tidy=TRUE, tidy.opts=list(indent=2, width.cutoff=55)
)

@@

@@

```{r anotherplot, fig.ncol=3, fig.cap='Other uninteresting plots', fig.subcap=month.name[1:6], out.width=Pmisc::out.width(0.32)}
